Using the Design Thinking Empathy Phase as a Facilitator in Privacy Requirements Elicitation

### 2020-02-20 paperRE2020.tex
Updates from Overleaf

\todo[inline]{aqui temos que descrever as que achamos na literatura -- Eu só consegui 3 -- Angelica você pode fechar essa questão?}

@@

>>>>

@@

%Segundo \cite{DBLP:conf/interact/WolfelM13}  existem vários exemplos de method cards, focados no design participativo e no desenvolvimento da empatia. Assim, esses methods poderiam ser considerados ferramentas de empatia. Esses method cards envolvem designers e usuários no processo. Alguns method cards são projetados para uma melhor comunicação entre usuários e designers, como por exemplo Questionable Concept Cards, IDEO method cards entre outros.

According to \cite{DBLP:conf/interact/WolfelM13} there are several examples of method cards, focused on participatory design and the development of empathy. Thus, these methods could be considered tools of Empathy. These method cards involve designers and users in the process. Some method cards are designed for better communication between users and designers, such as Questionable Concept Cards, IDEO method cards, among others.
